Golf-Sport: Managing Operations \\ A Case Study in Optimization

### 2018-05-03 Paper.tex
Final Draft
Needs to be proofread and touched up.  Otherwise complete.  Successfully typesets at this point.

Optimizing profit through production in processes is studied within the realm of the operations management. As the global market continues to grow and expand, businesses are focusing on remaining competitive. Erik Johannesson and Christian Karsten explain this best. ``Large organizations face thousands of planning problems every day. Some are simple, and decisions can be made quickly and efficiently by a single person. Others are on a different, larger scale which require much more effort, and they may also have a significant impact on the bottom line.  All of these decisions are interlinked, with the overall objective being to meet customer demand at the lowest overall cost” .\cite{johan}

@@

In a survey of optimization techniques being used within operations management, the authors broken the process into three distinct parts. These can be identified as input management, facilities management, and output management. Stated more simply, these correspond to scheduling, production, and vehicle routing, respectively. Failure to optimize any one of these areas can lead large inefficiencies (i.e. lost revenue) for a company. Making too much of one product leads to inventory costs. Failure to plan good routes leads to higher shipping costs. Not spending enough on advertising leads to missed opportunities. Johnannesson and Karsten go on to say, ``As such problems often have a large scale, the impact can be significant. For example, it is not uncommon to be able to decrease logistics spending by 5 to 10 percent in a supply chain with annual logistics costs of over \$100 million. 
Additionally, it can reduce the planning time from days to minutes. Thus, evaluation of multiple scenarios becomes feasible, and an automated decision-support tool may serve as an integral part of both operational and strategic decision making.”\cite{johan}  

@@

Optimizing profit through production in processes is studied within the realm of the operations management.  As the global market continues to grow and expand, businesses are focusing on remaining competitive.  In a survey of 
optimization techniques being used within operations management, the authors broken the process into three distinct parts.  These can be identified as input management, facilities management, and output management.  Stated more simply, these correspond to 
scheduling, production, and vehicle routing, respectively.  
Clearly there is a need for operations management to be optimized, especially as a business or problem grows more complex. Several approaches for operations management use genetic algorithms, especially when focusing on lot sizing within material requirements, aggregate and assortment planning, and facility layout problems \cite{gen}.  

@@

Generally speaking, many optimization problems can be converted into a linear programming model.  The drawback to this, however, can be extremely long and computationally expensive runtimes, depending on the solution space.  Klotz and Newman conducted research into this, and 
while they concluded that many operations management/production problems can be solved using linear programming, it may not be the best approach.  However, by adjusting settings and parameters in software-based solvers, many large-scale problems can be effectively solved in this way \cite{klotz}.  This Golf-Sport problem falls squarely within the facilities management/production sector.  Fei et al discovered that for large-scale production optimizations, heuristics were necessarily utilized.  Additionally, the most common solution approaches utilize branch-and-cut or branch-and-price \cite{survey}.

@@

Golf-Sport is a golf club manufacturing company with three plants in Arizona.  Each plant has an attached retail store and is treated as its
only supplier.  Each location has predicted minimum and maximum sales of each item type per period.  The goal of this optimization is to maximize profit over a two-month period by determining the optimal number of each product to make
at each location.  The solution will presented as three periods: (1) manufactured and sold in month one; (2) manufactured and sold in month two; and (3) manufactured in month one and sold in month two.  In this problem, two types of constraints exist:  local and global.  Local constraints are unique to each plant/store
 combination, while the global constraints refer to company-wide resources.  Initially, the problem will be modeled and optimized adhering strictly to the provided constraints and bounds.  The two-month period is set, with no information given as to the going concern of this company.  This two-month optimization can serve as a baseline, and could later be expanded to more periods if desired.  
 This particular problem appears to lend itself to integer programming as the ideal optimization method.  The problem will be coded and solved using MATLAB's optimization toolbox functionality.

@@

it is clearly stated that the amount of money earmarked for advertising each month will not carryover into the next month.  Graphite seems to have no such restriction, so 
it appears reasonable to incorporate the possibility of carryover of graphite stock.

@@

\subsection{Objective}
The objective of this model is to maximize profit, represented as the difference between sales revenue and cost.  For the purposes of this function let \textit{R, C \& I} represent revenue, product cost, and inventory cost, respectively.  The function can be expressed as:
%align functions to the left

@@

\section{Implementation}
\subsection{Hardware \& Software}
The problem was coded and solved in MATLAB R2017b on a personal computer.  The code does not appear to be backward-compatible due to the use of the \textit{optimproblem} implementation.  The small scale of this optimization does not necessitate a computer beyond average specifications.
\subsection{Algorithm}
This problem was solved using the \textit{intlinprog} function in MATLAB.  This function conducts a linear relaxation on the problem, in order to set the upper bound.  Then, the algorithm iterates through a branch-and-cut approach to solve for the optimal integer solution.  By default, the function 
will iterate through 1,000,000 iterations prior to terminating.  These iterations check the feasible solutions at the nodes along the tree created through branch-and-bound.  Additionally, the function applies basic heuristics in the form of Gomory cuts.  Gomory cuts are defined as an added constraint along a hyperplane to a vertex.  They are commonly implemented in most commercial integer programming solvers as an initial heuristic.  In optimization software implementations, these cuts tend to be accurate overall and invalid cuts are rarely made \cite{gomory}.  Given this knowledge, it is safe to assume that these cuts will not negatively affect the solution to this problem.

@@

This optimal production scenario generates a maximized profit of \$940,366 for Golf-Sport as a company in the two month period.  The linear relaxation yielded a global optimal profit of \$941,110, so this 
IP solution is valid (does not violate the Representation Theorem).  The problem does not provide a current company profit, so it is not known how much of an increase in potential profit this soution would yield.

@@

For example, the existing parameters seem to not account for maintaining a workforce and the minimum demand is set too low.  This analysis will adjust some of these parameters and constraints to produce a more 

@@

Second, the problem will be analyzed and adjusted to explore several range sensitivity topics.  This can help direct the business' focus and direction in order to further maximize profit potential.  Specifically, advertising dollars and graphite stock range sensitivity will be explored.  These are both areas in which Golf-Sport has considered contributing extra resources.  Additionally, a proposed advertising plan 

@@

Upon further examination and analysis of the model \& results, the current parameters do not appear to be as complete as possible.  While it exists only as a case study, several further parameters will be added in order to present a more realistic model and solution.  The added parameters will include:

@@

The addition of these parameters is necessary to model a more complete production problem.  First, the current model yields very uneven production amounts between periods.  While perhaps optimal, it would be unrealistic to recommend that a company lay off its workers if unnecessary.  Therefore, labor minimums will be set to 25\% of the current maximums.  Second, 
any production facility will incur fixed costs per month, regardless of production.  This will be included as a constraint:

@@

@@

profit of \$940,110.  This should help show Golf-Sport the importance of graphite to the operation, as it is a limiting factor on current profit.  It should be noted that when graphite is doubled in this case, excess stock exists at the end of the two-month period.  This suggests that with current demand and constraints, obtaining more than 2,000 pounds of graphite stock per month is unnecessary, 

>>>>

Optimizing profit through production in processes is studied within the realm of operations management. As the global market continues to grow and expand, businesses are focusing on remaining competitive. Erik Johannesson and Christian Karsten explain this best. ``Large organizations face thousands of planning problems every day. Some are simple, and decisions can be made quickly and efficiently by a single person. Others are on a different, larger scale which require much more effort, and they may also have a significant impact on the bottom line.  All of these decisions are interlinked, with the overall objective being to meet customer demand at the lowest overall cost."\cite{johan}

@@

In a survey of optimization techniques being used within operations management, the authors have broken the process into three distinct parts. These can be identified as input management, facilities management, and output management. Stated more simply, these correspond to scheduling, production, and vehicle routing, respectively. Failure to optimize any one of these areas can lead large inefficiencies (i.e. lost revenue) for a company. Making too much of one product leads to inventory costs, failure to plan good routes leads to higher shipping costs, and not spending enough on advertising leads to missed opportunities and subpar performance. Johnannesson and Karsten go on to say, ``As such problems often have a large scale, the impact can be significant. For example, it is not uncommon to be able to decrease logistics spending by 5 to 10 percent in a supply chain with annual logistics costs of over \$100 million. 
Additionally, it can reduce the planning time from days to minutes. Thus, evaluation of multiple scenarios becomes feasible, and an automated decision-support tool may serve as an integral part of both operational and strategic decision making."\cite{johan}  

@@

There is a clear need for operations management to be optimized, especially as a business or problem grows more complex. Several approaches for operations management use genetic algorithms, especially when focusing on lot sizing within material requirements, aggregate and assortment planning, and facility layout problems \cite{gen}.  

@@

Generally speaking, many optimization problems can be converted into a linear programming model.  The drawback to this, however, can be extremely long and have computationally expensive runtimes, depending on the solution space.  Klotz and Newman conducted research into this, and 
while they concluded that many operations management/production problems can be solved using linear programming, it may not always be the best approach.  However, by adjusting settings and parameters in software-based solvers, many large-scale problems can be effectively solved in this way \cite{klotz}.  This Golf-Sport problem falls squarely within the facilities management/production sector.  Fei et al discovered that for large-scale production optimizations, heuristics were necessarily utilized.  Additionally, the most common solution approaches utilize branch-and-cut or branch-and-price \cite{survey}.

@@

Golf-Sport is a small-sized company that produces high-quality components for people who build their own golf clubs and prebuilt sets of clubs. There are five components—steel shafts, graphite shafts, forged iron heads, metal wood heads, and metal wood heads with titanium inserts—made in three plants—Chandler, Glendale, and Tucson—in the Golf-Sport system. Each plant can produce any of the components, although each plant has a different set of individual constraints and unit costs. These constraints cover labor and packaging machine time (the machine is used by all components). Note that even though the components are identical in the three plants, different production processes are used, and therefore the products use different amounts of resources in different plants.
Besides component sales, the company takes the components and manufactures sets of golf clubs. Each set requires 13 shafts, 10 iron heads, and 3 wood heads. All of the shafts in a set must be the same type (steel or graphite), and all of the wood heads must be the same type (metal or metal with inserts). Each plant has unique assembly times.
Each plant of Golf-Sport has a retail outlet to sell components and sets, and the specific plant is the only supplier for its retail outlet. The minimum and maximum amounts of demand for each plant–product pair are unique. Note that, although the minimums must be satisfied, you do not need to satisfy demand up to the maximum amount.
This planning problem is for two months. The material, production, and assembly costs increase by 12\% for the second month, and production times are stationary. Inventory costs are based on end-of-period inventory for each product set and cost out at 8\% of the cost values of material, production and assembly. Additionally, each product generates different revenue depending on where it is made. Initially, there is no inventory.
The corporation controls the capital available or expenses; the cash requirements for each product are given. There is a total of \$20,000 available for advertising for the entire system during each month, and any money not spent in a month is not available the next month. The corporation also controls graphite. Each shaft requires 4 ounces of graphite; a total of 1,000 pounds is available for each of the two months. 
The goal is to determine a recommendation for the company. A recommendation includes a plan for production and sales. Additionally, the following sensitivity-analysis issues were explored:
	\item How can the problem be modeled to present a more complete picture of a manufacturer’s operations?
	\item How does more advertising budget or graphite affect the outcome?
	\item 	Marketing is trying to get Golf-Sport to consider an advertising program that promises a 50\% increase in their maximum demand. Can the 		current system be utilized to increase profit with this new scheme?
The solution will presented as three options for production and sales: (1) manufactured and sold in month one; (2) manufactured and sold in month two; and (3) manufactured in month one and sold in month two. In this problem, two types of constraints exist: local and global. This two-month optimization can serve as a baseline and could later be expanded to more periods if desired. This particular problem appears to lend itself to integer programming as the ideal optimization method. The problem will be coded and solved using MATLAB’s optimization toolbox functionality.

@@

it is clearly stated that the amount of money earmarked for advertising each month will not carryover into the next month.  Graphite has no such restriction, so 
it seems reasonable to incorporate the possibility of carryover of graphite stock.

@@

\subsection{Objective}
The objective of this model is to maximize profit, represented as the difference between sales revenue and cost.  For the purposes of this function let \textit{R, C} \& \textit{I} represent revenue, product cost, and inventory cost, respectively.  The function can be expressed as:
%align functions to the left

@@

\section{Implementation}
\subsection{Hardware \& Software}
The problem was coded and solved in MATLAB R2017b on a personal computer.  The code does not appear to be backward-compatible due to the use of the \textit{optimproblem} implementation.  The small scale of this optimization does not necessitate a computer beyond average specifications.
\subsection{Algorithm}
This problem was solved using the \textit{intlinprog} function in MATLAB.  This function initially conducts a linear relaxation on the problem, in order to set the upper bound.  Then, the algorithm iterates through a branch-and-cut approach to solve for the optimal integer solution.  By default, the function 
will iterate through 1,000,000 iterations prior to terminating or until the gap tolerance is met.  These iterations check the feasible solutions at the nodes along the tree created through branch-and-bound.  Additionally, the function applies basic heuristics in the form of Gomory cuts.  Gomory cuts are defined as an added constraint along a hyperplane to a vertex.  They are commonly implemented in most commercial integer programming solvers as an initial heuristic.  In optimization software implementations, these cuts tend to be accurate overall and invalid cuts are rarely made \cite{gomory}.  Given this knowledge, it is safe to assume that these cuts will not negatively affect the solution to this problem.

@@

This optimal production scenario generates a maximized profit of \$940,366 for Golf-Sport as a company in the two month period.  The linear relaxation yielded a global optimal profit of \$941,110, so this 
IP solution is valid (because it does not violate the Representation Theorem).  The problem does not provide a current company profit prior to this optimization.  Therefore, it is not known how this production scheme compares to the company's current production and profit.

@@

For example, the existing parameters seem to not account for maintaining a workforce and the minimum demand is set too low to stock the shelves of a retail outlet.  This analysis will adjust some of these parameters and constraints to produce a more 

@@

Secondly, the problem will be analyzed and adjusted to explore several range sensitivity topics.  This can help direct the business' focus and direction in order to further maximize profit potential.  Specifically, advertising dollars and graphite stock range sensitivity will be explored.  These are both areas in which Golf-Sport has considered contributing extra resources.  Additionally, a proposed advertising plan 

@@

Upon further examination and analysis of the model \& results, the current parameters do not appear to be as complete as possible when representing a manufacturing company.  While it exists only as a case study, several further parameters will be added in order to present a more realistic model and solution.  The added parameters will include:

@@

The addition of these parameters is necessary to model a more complete production problem.  First, the current model yields very uneven production amounts between periods.  While perhaps optimal, it would be unrealistic to recommend that a company lay off its workers if unnecessary.  Therefore, labor minimums will be set to 25\% of the current maximums.
Second, any production facility will incur fixed costs per month, regardless of production.  This will be included as a constraint:

@@

\section{Range Analysis}

@@

profit of \$941,110.  This should help show Golf-Sport the importance of graphite to the operation, as it is a limiting factor on current profit.  It should be noted that when graphite is doubled in this case, excess stock exists at the end of the two-month period.  This suggests that with current demand and constraints, obtaining more than 2,000 pounds of graphite stock per month is unnecessary, 
